---
title: "Automated Subtitling Market Segmentation"
author: "Ryan Lord"
date: "2025-03-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Check if required packages are installed and install if necessary. 
Add packages to library. 
```{r,warning=FALSE}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("tidyverse", quietly = TRUE)) {
  install.packages("tidyverse")
}
if (!requireNamespace("readr", quietly = TRUE)) {
  install.packages("readr")
}
if (!requireNamespace("treemapify", quietly = TRUE)) {
  install.packages("treemapify")
}
if (!requireNamespace("DT", quietly = TRUE)) {
  install.packages("DT")
}


library(ggplot2)    # data visualisation
library(tidyverse)  # data wrangling
library(readr)      # import .csv from github
library(treemapify) # create tree maps
library(DT)         # nicely formatted tables


```



Import data from our github repo: https://github.com/NHS-Ryan/windmill_mov_subtitles
Some small data cleaning required to account for NULL values in the country_information.csv file
```{r, warning=FALSE}

country_information <- read_csv("https://raw.githubusercontent.com/NHS-Ryan/windmill_mov_subtitles/refs/heads/main/country_information.csv")
supported_languages <- read_csv("https://raw.githubusercontent.com/NHS-Ryan/windmill_mov_subtitles/refs/heads/main/supported_languages.csv")


head(country_information)
head(supported_languages)

```



Join to Windmill Pictures' Supported Languages information so we can exclude countries with languages we are already working with. 
```{r}

supported_languages$supported_language_flag = 0

country_information <- left_join(country_information, supported_languages, 
                                 by = c("primary_language" = "supported_languages")
                                 )

# Disable scientific notation for values
options(scipen = 999) 


# Replace "NULL" strings with 0 in english_speakers_l1 & convert to numeric
country_information$english_speakers_l1[country_information$english_speakers_l1 == "NULL"] <- 0
country_information$english_speakers_l1 <- as.numeric(country_information$english_speakers_l1)

# Replace "NULL" strings with 0 in english_speakers_l2 & convert to numeric
country_information$english_speakers_l2[country_information$english_speakers_l2 == "NULL"] <- 0
country_information$english_speakers_l2 <- as.numeric(country_information$english_speakers_l2)

# Create English Speakers total as a sum of l1 + l2 columns
country_information$english_speakers_total <- 
  country_information$english_speakers_l1 + country_information$english_speakers_l2

country_information$supported_language_flag <- country_information$supported_language_flag %>%
  replace_na(1)

country_information

```


We now want to do the final work to prepare our data to create our market_score. Market Score is a score out of 10 where a country scoring a full 10 points would have the largest population, highest median income & strong 5 year GDP growth:

The market score takes 3 parameters: target_population ,average_gdp_change_5_years & median_income. 

2 of the parameters are already available in our country_information dataframe, but target_population needs to be calculated as follows: 

target_population = supported_language_flag * (primarly_language_speakers - (english_speakers_l1 + english_speakers_l2))
median_income

We then take the 3 parameters, rank them from highest to lowest, and normalise the result from 0 to 1. Finally we apply the following weights to give a final score out of 10: 
average_gdp_change_5_years_norm * 2.5 + 
median_income * 2.5 + 
target_population * 5 + 
= market_score

```{r}

normalise <- function(x) {
  return((x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE)))
}

country_information$median_income_score <-
  normalise(rank(country_information$median_income)) * 3.5

country_information$avg_gdp_change_5_years_score <-
  normalise(rank(country_information$avg_gdp_change_5_years)) * 2.5

country_information$target_population_score <-
  normalise(rank(country_information$supported_language_flag * 
  (
    (
    (country_information$population * country_information$primary_language_speakers) - 
      country_information$english_speakers_total
    )
   )
  )
  ) * 4

country_information$market_score <-
  (country_information$median_income_score + 
     country_information$avg_gdp_change_5_years_score +
     country_information$target_population_score) *
  country_information$supported_language_flag


```



Create a Treemap of languages including an 'unsupported_languages' category to demonstrate how much of the overall global market we are missing. 
```{r}

temp_df <- data.frame(primary_language = character(),
                      total_value = numeric())

unsupported_val = (country_information %>%
         filter(supported_language_flag == 1) %>%
         summarize(total_value = sum(population)))$total_value[1]

temp_df <- temp_df %>% add_row(
  primary_language = "Unsupported Languages",
  total_value = unsupported_val)

country_information %>%
  select(country,population,
         primary_language,supported_language_flag) %>%
  filter(supported_language_flag == 0) %>%
  group_by(primary_language) %>%
  summarise(total_value = sum(population, na.rm = TRUE)) %>%
  add_row(temp_df) %>%
  mutate(primary_language = str_to_title(primary_language)) %>%
  group_by(primary_language) %>%
  summarise(total_value = (total_value = sum(round(total_value / 1000000,0)))) %>%
  arrange(desc(total_value)) %>%
  ggplot(aes(area = total_value, fill = primary_language,
               label = paste(primary_language, total_value, 
                             sep = "\n"))) +
    geom_treemap() +
    geom_treemap_text(colour = "white",
                      place = "topleft",
                      size = 15) +
    theme(legend.position = "none") +
    scale_fill_brewer(palette = "Reds") +
    labs(title = "Millions of Speakers...")
```



Nicely formatted datatable with market_score:
```{r}
country_information %>%
  select(country,primary_language,market_score) %>%
  mutate(market_score = round(country_information$market_score,1)) %>%
  filter(market_score > 0) %>%
  arrange(desc(market_score)) %>%
  datatable(options = list(pageLength = 5, autoWidth = TRUE)) %>%
  formatStyle(
    'market_score',
    background = styleColorBar(country_information$market_score, 'red'),
    backgroundSize = '100% 100%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )
```

Raw scores table: 
```{r}

country_information %>%
  select(country,population, primary_language_speakers,english_speakers_total,median_income,avg_gdp_change_5_years,market_score) %>%
  mutate(market_score = round(country_information$market_score,1)) %>%
  filter(market_score > 0) %>%
  arrange(desc(market_score)) %>%
  datatable(options = list(pageLength = 5, autoWidth = TRUE)) %>%
  formatStyle(
    'market_score',
    background = styleColorBar(country_information$market_score, 'red'),
    backgroundSize = '100% 100%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )


```



Composite scores table
```{r}
country_information %>%
  select(country,median_income_score, target_population_score ,english_speakers_total,avg_gdp_change_5_years_score,market_score) %>%
  mutate(market_score = round(country_information$market_score,1)) %>%
  filter(market_score > 0) %>%
  arrange(desc(market_score)) %>%
  datatable(options = list(pageLength = 5, autoWidth = TRUE)) %>%
  formatStyle(
    'market_score',
    background = styleColorBar(country_information$market_score, 'red'),
    backgroundSize = '100% 100%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )
```



